---
title: "ETF Ownership"
author: "Jonathan Alexander Zeh"
date: "`r Sys.Date()`"
output:
  pdf_document:
  #html_document:
    #theme: cerulean
    #mainfont: Monaco
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(ggplot2)
library(caTools)
library(dplyr)
library(purrr)
library(knitr)
library(readxl)
library(DescTools)
library(fixest)
```

# data preperation functions
## data import
```{r, include = F}
data_import_func <- function(subset = "none"){
  if(subset == "none"){
    df_raw = read_csv("/Users/jonathanzeh/Library/CloudStorage/OneDrive-Personal/BA_Thesis/BA_coding/datasets/eikon_data/variable_data/monthly_panel_v1.csv")
  }
  if(subset == "europe"){
    df_raw = read_csv("/Users/jonathanzeh/Library/CloudStorage/OneDrive-Personal/BA_Thesis/BA_coding/datasets/eikon_data/variable_data/monthly_panel_v1_europe.csv")
  }

  df_raw$date <- as.Date(df_raw$date)
  return(df)
}
```
## data manipulation
### Outliers
```{r}
replace_outliers_with_na <- function(data, variable_name, threshold) {
  outlier_rows <- which(data[[variable_name]] > threshold)

  # replace entire rows with NA where an outlier is detected
  if (length(outlier_rows) > 0) {
    data[outlier_rows, -(1:3)] <- NA
  }

  return(data)
}

apply_outliers_func <- function(){
  df <- replace_outliers_with_na(df, "ETF_ownership", 0.3)
  df <- replace_outliers_with_na(df, "percent_of_traded_shares", 30)
  df <- replace_outliers_with_na(df, "FUND_percent_of_traded_shares", 80)
  df <- replace_outliers_with_na(df, "FUND_ownership", 0.8)
  return(df)
}
```

### Change zero values to NA
```{r}
handle_zero_vals_func <- function(){
  df$percent_of_traded_shares[df$percent_of_traded_shares == 0] <- NA
  df$ETF_ownership[df$ETF_ownership == 0] <- NA
  df$market_cap[df$market_cap == 0] <- NA
  df$amihud_ratio[is.infinite(df$amihud_ratio)] <- NA
  df$monthly_std_dev[df$count_returns < 15] <- NA
  return(df)
}
```

### Min Number of Observations
```{r}
min_obersevations_func <- function(){
  #lets only allow stocks with more than 12 observations
  df$stock_RIC <- as.factor(df$stock_RIC)

  observation_count <- df %>%
    mutate(observation = ifelse(is.na(monthly_std_dev) == TRUE, 0, 1)) %>%
    group_by(stock_RIC) %>%
    summarise(n_observations = sum(observation)) %>%
    filter(n_observations >= 12)
              
  ### only keep observations that are in this data frame
  stocks_to_keep <- observation_count$stock_RIC
  df <- df %>%
    filter(stock_RIC %in% stocks_to_keep)
 return(df) 
}
```

### Construct Variables
```{r}
var_construction_func <- function(){
  df <- df %>%
  mutate(log_market_cap = log(market_cap),
         inv_price = 1/price,
         index_member_600_ex_50 = ifelse(
           index_member_600 == 1 & index_member_50 == 0, 1, 0))
  return(df)
}
```

### Handle NAs for Standardization
```{r}
# Define the function
set_row_na_if_any_na_func <- function(df) {
  
  columns_not_to_set_na <- c("date", "stock_RIC", "index_member_600",
                             "index_member_50",
                             "index_member_600_ex_50", "year_month")
  columns_to_check <- c("percent_of_traded_shares", "FUND_percent_of_traded_shares",
                      "INDEX_FUND_percent_of_traded_shares",
                       "ACTIVE_FUND_percent_of_traded_shares",
                       "log_market_cap", "inv_price", "amihud_ratio",
                      "monthly_relative_spread", "monthly_std_dev",
                      "T1_monthly_std_dev","T2_monthly_std_dev",
                      "T3_monthly_std_dev")
  
  
  # Get all column names
  all_columns <- colnames(df)
  
  # Determine columns to set to NA by excluding columns_not_to_set_na
  columns_to_set_na <- setdiff(all_columns, columns_not_to_set_na)
  
  # Create a logical vector to identify rows with NA in the columns_to_check
  rows_with_na <- rowSums(is.na(df[, columns_to_check])) > 0
  
  # Set the specified columns to NA for the identified rows
  df[rows_with_na, columns_to_set_na] <- NA
  
  return(df)
}
```

### Index Subsets
```{r}
# define winsorize function
winsorize_var <- function(x, probs = c(0.02, 0.98)) {
  Winsorize(x, probs = probs, na.rm = TRUE)
}

# take subsets for different index specifications
non_index_members_to_NA <- function(col_name, data) {
  outlier_rows <- which(data[[col_name]] == 0)

  # replace entire rows with NA where an outlier is detected
  if (length(outlier_rows) > 0) {
    data[outlier_rows, -(1:4)] <- NA
  }
  
  data <- data %>%
    group_by(stock_RIC) %>%
    mutate(final_ETF_ownership = 
           scale(winsorize_var(percent_of_traded_shares/100)),
         final_FUND_ownership =
           scale(winsorize_var(FUND_percent_of_traded_shares/100)),
         final_INDEX_FUND_ownership =
           scale(winsorize_var(INDEX_FUND_percent_of_traded_shares/100)),
         final_ACTIVE_FUND_ownership =
           scale(winsorize_var(ACTIVE_FUND_percent_of_traded_shares/100)),
         final_monthly_std_dev = scale(winsorize_var(monthly_std_dev)),
         final_T1_monthly_std_dev = scale(winsorize_var(T1_monthly_std_dev)),
         final_T2_monthly_std_dev = scale(winsorize_var(T2_monthly_std_dev)),
         final_T3_monthly_std_dev = scale(winsorize_var(T3_monthly_std_dev)))
  
  return(data)
}
```


# Main Data Preperation
```{r}
main <- function(subset = "none"){
  df <- data_import_func(subset)
  df <- apply_outliers_func()
  df <- handle_zero_vals_func()
  df <- min_obersevations_func()
  df <- var_construction_func()
  df <- set_row_na_if_any_na_func()
  return(df)
}
```

## Subset: None
```{r}
df <- main(subset = "none")

df_600 <- non_index_members_to_NA("index_member_600", df)
df_600_ex_50 <- non_index_members_to_NA("index_member_600_ex_50", df)
df_50 <- non_index_members_to_NA("index_member_50", df)
```

## Subset: Europe
```{r}
df_eu <- main(subset = "europe")

df_600_eu <- non_index_members_to_NA("index_member_600", df_eu)
df_600_ex_50_eu <- non_index_members_to_NA("index_member_600_ex_50", df_eu)
df_50_eu <- non_index_members_to_NA("index_member_50", df_eu)
```


# statistics
## Summary Statistics
```{r}
## data: df_outstanding
library(dplyr)
library(tidyr)

calculate_summary_statistics <- function(df, row_names) {
  df_summary_statistics <- tibble(
    n = rep(nrow(df_summary), ncol(df_summary)),
    mean = sapply(df_summary, mean, na.rm=TRUE),
    sd = sapply(df_summary, sd),
    min = sapply(df_summary, min),
    median = sapply(df_summary, median),
    max = sapply(df_summary, max)) %>%
      round(3)
  
  df_summary_statistics <- data.frame(df_summary_statistics)
  rownames(df_summary_statistics) <- row_names 


  return(df_summary_statistics)
}

# List of variables to include
row_names <- c("Daily Volatility", "ETF ownership", "log(Mktcap)", 
               "1/Price", "Amihud", 
               "Bid-ask spread", "Past 12-month returns", "Fund ownership", 
               "Index fund ownership", "Active fund ownership")

df_f <- df_outstanding[, -c(2)]
df_summary <- df_f %>%
    select(monthly_std_dev, ETF_ownership, log_market_cap,
           inv_price, amihud_ratio, monthly_relative_spread,
           cumulative_return_12m, FUND_ownership,
           INDEX_FUND_ownership, ACTIVE_FUND_ownership) %>%
  na.omit()

df_summary_statistics <- calculate_summary_statistics(df_summary, row_names)

########## exporting as tex file
library(stargazer)

summary_text = "The table presents the statistics for variables used in this study. The sample covers the periode from January 2010 to December 2023. This data contain survior-ship bias for stocks, that are no longer listed."

stargazer(df_summary_statistics, type = "latex", 
          title = "Summary Statistics for Monthly Sample",
          summary = FALSE,
          header = FALSE,
          out = "/Users/jonathanzeh/Library/CloudStorage/OneDrive-Personal/BA_Thesis/BA_coding/R_exports/summary_statistics/summary_statistics.tex")
```

## correlation matrix
```{r}

df_corr <- df_outstanding %>%
  group_by(stock_RIC) %>%
  summarize(change_ETF = diff(percent_of_traded_shares),
            change_INDEX_FUND = diff(INDEX_FUND_percent_of_traded_shares),
            change_ACTIVE_FUND = diff(ACTIVE_FUND_percent_of_traded_shares)) %>%
  na.omit()

df_f <- df_corr[, -c(1)]
df_summary <- df_f %>%
    select(final_monthly_std_dev, ETF_ownership, log_market_cap,
           inv_price, amihud_ratio, monthly_relative_spread,
           cumulative_return_12m, final_FUND_ownership,
           final_INDEX_FUND_ownership, final_ACTIVE_FUND_ownership) %>%
  na.omit()






cor_df <- as.data.frame(cor(df_f))
rownames(cor_df) <- rownames(df_summary_statistics)

cor_df
```


# regression
## regression function
```{r}
library(fixest)
library(dplyr)

fe_function <- function(df, 
                        indep_vars, fixed_vars,
                        periode_vec,
                        setup = setup,
                        volatility_lag = FALSE, 
                        fund_consolidation = FALSE){
  ################################################### sample split by period
  df_f <- df %>%
    mutate(year = as.numeric(format(date, "%Y"))) %>%
    filter(periode_vec[1] <= year & year < periode_vec[2]) 
  
  df_f <- df_f %>%
    group_by(stock_RIC) %>%
    mutate(final_ETF_ownership = 
           scale(winsorize_var(percent_of_traded_shares/100)),
         final_FUND_ownership =
           scale(winsorize_var(FUND_percent_of_traded_shares/100)),
         final_INDEX_FUND_ownership =
           scale(winsorize_var(INDEX_FUND_percent_of_traded_shares/100)),
         final_ACTIVE_FUND_ownership =
           scale(winsorize_var(ACTIVE_FUND_percent_of_traded_shares/100)),
         final_monthly_std_dev = scale(winsorize_var(monthly_std_dev)),
         final_T1_monthly_std_dev = scale(winsorize_var(T1_monthly_std_dev)),
         final_T2_monthly_std_dev = scale(winsorize_var(T2_monthly_std_dev)),
         final_T3_monthly_std_dev = scale(winsorize_var(T3_monthly_std_dev)))
    
  ####################################################### subset
  if(setup == "lag_fund"){
    vars_to_exclude <- c()    
    if(volatility_lag == FALSE){
      vars_to_exclude <- c(vars_to_exclude, 
                           "final_T1_monthly_std_dev",
                           "final_T2_monthly_std_dev",
                           "final_T3_monthly_std_dev")
    }
    if(fund_consolidation == TRUE){
      vars_to_exclude <- c(vars_to_exclude, 
                           "final_INDEX_FUND_ownership",
                           "final_ACTIVE_FUND_ownership")
    }
    if(fund_consolidation == FALSE){
      vars_to_exclude <- c(vars_to_exclude,
                           "final_FUND_ownership")
    }
    indep_vars <- indep_vars[!indep_vars %in% vars_to_exclude]
  }
  
  if(setup == "lag"){
    vars_to_exclude <- c() 
    if(volatility_lag == FALSE){
      vars_to_exclude <- c(vars_to_exclude, 
                           "final_T1_monthly_std_dev",
                           "final_T2_monthly_std_dev",
                           "final_T3_monthly_std_dev")
    }
    indep_vars <- indep_vars[!indep_vars %in% vars_to_exclude]
  }
  
  if(setup == "fund"){
    vars_to_exclude <- c() 
    if(fund_consolidation == TRUE){
      vars_to_exclude <- c(vars_to_exclude, 
                           "final_INDEX_FUND_ownership",
                           "final_ACTIVE_FUND_ownership")
    }
    if(fund_consolidation == FALSE){
      vars_to_exclude <- c(vars_to_exclude,
                           "final_FUND_ownership")
    }
    indep_vars <- indep_vars[!indep_vars %in% vars_to_exclude]
  }

  ####################################################### formula string
  indep_vars_string <- paste(indep_vars, collapse = " + ")
  fixed_effects_string <- paste(fixed_vars, collapse = " + ")
  
  if(all(is.na(fixed_vars)) == TRUE){
    formula_string <- paste("final_monthly_std_dev ~", 
                          indep_vars_string)
  } else {
    formula_string <- paste("final_monthly_std_dev ~", 
                          indep_vars_string, "|", 
                          fixed_effects_string)
  }
  
  model_formula <- as.formula(formula_string)
  
  ####################################################### data prep
  df_f$date <- as.Date(df_f$date)
  df_f$stock_RIC <- as.factor(df_f$stock_RIC)
  df_f$month <- as.factor(format(df_f$date, "%m"))
  df_f$year <- as.factor(df_f$year)
  df_f$quarter <- as.factor(quarters(df_f$date))
  
  ####################################################### regression
  fe_model <- feols(model_formula, data = df_f)
  
  return(fe_model)
}
```

## implement fixed effects function
```{r}
data_on_fe_function <- function(df, indep_vars, fixed_vars, periode_list,
                                single_setup = FALSE){
  
  generate_models <- function(period, df, indep_vars, fixed_vars, 
                              single_setup){
    
    if(single_setup == FALSE){
      list(fe_model = fe_function(df, indep_vars, fixed_vars, period, 
                                volatility_lag = FALSE),
           fe_model_lag = fe_function(df, indep_vars, fixed_vars, period, 
                                 volatility_lag = TRUE))
    } else if (single_setup == TRUE) {
      list(fe_model = fe_function(df, indep_vars, fixed_vars, period, 
                             volatility_lag = TRUE))
    }
  }

  models <- lapply(periode_list, generate_models, 
                   df = df, indep_vars = indep_vars, fixed_vars = fixed_vars,
                   single_setup = single_setup)
  
  if(single_setup == FALSE){
    fe_models_list <- setNames(
    do.call(c, models), 
    c(sapply(periode_list,
             function(p) paste("fe_model", 
                               paste(p, collapse = "_"), sep = "_")),
      sapply(periode_list, function(p) paste("fe_model", 
                                             paste(p, collapse = "_"), "
                                             lag", sep = "_"))))
  } else {
    fe_models_list <- setNames(
    do.call(c, models), 
    c(sapply(periode_list,
             function(p) paste("fe_model", 
                               paste(p, collapse = "-"), sep = "_"))))
  }
  
  
  return(fe_models_list)
}
```

## new function
```{r}
data_on_fe_function <- function(df, indep_vars, fixed_vars, 
                                periode_list, setup = "lag") {
  generate_models <- function(period, df, indep_vars, fixed_vars, setup) {
    models_list <- list()
    
    # Add base model
    if(setup == "single"){
      models_list[['fe_model']] <- fe_function(
      df, indep_vars, fixed_vars, period, setup)
    } else if(setup == "lag"){
      models_list[['fe_model']] <- fe_function(
      df, indep_vars, fixed_vars, period, setup, volatility_lag = FALSE)
    } else if(setup == "fund"){
      models_list[['fe_model']] <- fe_function(
      df, indep_vars, fixed_vars, period, setup, fund_consolidation = FALSE)
    } else {
      models_list[['fe_model']] <- fe_function(
      df, indep_vars, fixed_vars, period, setup, volatility_lag = FALSE,
      fund_consolidation = FALSE)
    }
    
    
    if(setup == "lag" || setup == "lag_fund") {
      # Add lag model
      models_list[['fe_model_lag']] <- fe_function(
        df, indep_vars, fixed_vars, period, setup, volatility_lag = TRUE,
        fund_consolidation = FALSE)
    }
    
    if(setup == "fund" || setup == "lag_fund") {
      # Add fund model
      models_list[['fe_model_fund']] <- fe_function(
        df, indep_vars, fixed_vars, period, setup, 
        volatility_lag = TRUE, fund_consolidation = TRUE)
    }
    
    return(models_list)
  }
  
  # Generate models for each period
  models <- lapply(periode_list, generate_models, df = df, 
                   indep_vars = indep_vars, fixed_vars = fixed_vars, 
                   setup = setup)
  
  model_names <- c()
  fe_models_list <- list()
  
  for (i in seq_along(models)) {
    for (model_type in names(models[[i]])) {
      model_name <- paste("fe_model", i, model_type, sep = "_")
      fe_models_list[[model_name]] <- models[[i]][[model_type]]
      model_names <- c(model_names, model_name)
    }
  }
  names(fe_models_list) <- model_names
  
  return(fe_models_list)
}
```



## etable function
```{r}
library(fixest)
library(tinytex)
library(pdftools)

style_df <- style.df(depvar.title = "", fixef.title = "", stats.title = "",
                     yesNo = c("Yes", "No"))

etable_function <- function(fe_models_list, cluster = NA, 
                            title, sub_sample,
                            subfolder, file_name) {
  
  ######################## path string
  folder_path = "/Users/jonathanzeh/Library/CloudStorage/OneDrive-Personal/BA_Thesis/BA_coding/R_exports/regression_outputs/"
  
  output_path = paste0(folder_path, subfolder, "/", file_name)
  
  ######################## title string
  string_representation <- sapply(sub_sample, 
                                  function(x) paste(x, collapse = ","))
  subsample_string <- paste(string_representation, collapse = "; ")
  title <- paste(title, "Sub Sample:", subsample_string)
  
  ######################## variable labels
  variable_labels <- c(final_monthly_std_dev = "Daily Volatility", 
  final_ETF_ownership = "ETF ownership",
  log_market_cap = "log(Mktcap t-1)",
  inv_price = "1/Price t-1", 
  amihud_ratio = "Amihud t-1", 
  monthly_relative_spread = "Bid-ask spread t-1",
  price_to_BV = "Price to book t-1",
  cumulative_return_12m = "Past 12-month returns t-1",
  gross_profit = "Gross profitability t-1",
  final_FUND_ownership = "Fund ownership t-1",
  final_INDEX_FUND_ownership = "Index fund ownership t-1",
  final_ACTIVE_FUND_ownership = "Active fund ownership t-1",
  final_T1_monthly_std_dev = "Volatility t-1", 
  final_T2_monthly_std_dev = "Volatility t-2",
  final_T3_monthly_std_dev = "Volatility t-3"
  )
  
  ######################## etable
  if(all(is.na(cluster)) == FALSE){
    cluster_string = paste0("~", paste(cluster, collapse = " + "))
    etable(fe_models_list,
         cluster = cluster_string, 
         title = title,
         dict = variable_labels,
         fitstat = ~ r2 + n,
         style.df = style_df,
         view = TRUE,
         file = output_path)
  } else {
    etable(fe_models_list,
         title = title,
         dict = variable_labels,
         fitstat = ~ r2 + n,
         style.df = style_df,
         view = TRUE,
         file = output_path)
  }
}
```


## running regressions
### first models
```{r, echo = False}
#################################################################
# Data: df, Index: FALSE
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_FUND_ownership", 
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

periode_list <- list(c(2010, 2020), c(2020, 2021), c(2021, 2023))
fe_models_list_1 <- data_on_fe_function(df, indep_vars, fixed_vars, periode_list)

etable_function(fe_models_list_1,
                   "Data: df, Index: FALSE, Fund Split: FALSE",
                   "2024_05_26",
                   "table_df.tex")

#################################################################
# Data: df_index, Index: TRUE
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_FUND_ownership", 
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

periode_list <- list(c(2010, 2020), c(2020, 2021), c(2021, 2023))
fe_models_list_2 <- data_on_fe_function(df_index, indep_vars, fixed_vars,
                                        periode_list)

etable_function(fe_models_list_2,
                   "Data: df, Index: TRUE, Fund Split: FALSE",
                   "2024_05_26",
                   "table_df_index.tex")

#################################################################
# Data: df, Index: TRUE, Fund Split: TRUE
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership", 
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

periode_list <- list(c(2010, 2020), c(2020, 2021), c(2021, 2023))
fe_models_list_3 <- data_on_fe_function(df_index, indep_vars, fixed_vars,
                                        periode_list)

etable_function(fe_models_list_3,
                   "Data: df, Index: TRUE, Fund Split: TRUE",
                   "2024_05_26",
                   "table_df_index_fund_split.tex")

#################################################################
# Data: df_outstanding, Index: TRUE, Fund Split: TRUE
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership", 
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

periode_list <- list(c(2010, 2020), c(2020, 2021), c(2021, 2023))
fe_models_list_4 <- data_on_fe_function(df_outstanding, indep_vars, fixed_vars,
                                        periode_list)

etable_function(fe_models_list_4,
                   "Data: df_outstanding, Index: TRUE, Fund Split: TRUE",
                   "2024_05_26",
                   "table_df_oustanding_fund_split.tex")


#################################################################
# Data: df_outstanding, Index: TRUE, Fund Split: TRUE, 2014
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership", 
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

periode_list <- list(c(2010, 2020), c(2020, 2021), c(2021, 2024))

fe_models_list_5 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        periode_list)
etable_function(fe_models_list_5,
                   "Data: df_outstanding, Index: TRUE, Fund Split: TRUE,
                 Periods: 2014 to 2019, 2020, 2021 to 2023",
                   "2024_05_26",
                   "table_5_df_oustanding.tex")

```

### Full sample
```{r}
full_sample_function <- function(data_set, etable_title, file_name){
  periode_list <- list(c(2011, 2024))
  fixed_vars <- c("stock_RIC", "month", "headquarters_country")

#################################################################
# Setup 1
#################################################################
  indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m")

  fe_models_list_1 <- data_on_fe_function(data_set, indep_vars, fixed_vars,
                                          periode_list, setup = "single")

#################################################################
# Setup 2
#################################################################
  indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m", "final_FUND_ownership")
  fe_models_list_2 <- data_on_fe_function(
  data_set, indep_vars, fixed_vars, periode_list, setup = "single")

#################################################################
# Setup 3
#################################################################
  indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m", "final_INDEX_FUND_ownership", 
                "final_ACTIVE_FUND_ownership")

  fe_models_list_3 <- data_on_fe_function(
  data_set, indep_vars, fixed_vars, periode_list, setup = "single")

#################################################################
# Setup 4
#################################################################
  indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m", "final_INDEX_FUND_ownership", 
                "final_ACTIVE_FUND_ownership", "final_T1_monthly_std_dev",
                "final_T2_monthly_std_dev", "final_T3_monthly_std_dev")

  fe_models_list_4 <- data_on_fe_function(
  data_set, indep_vars, fixed_vars, periode_list, setup = "single")

#################################################################
  combined <- list(fe_models_list_1[[1]], fe_models_list_2[[1]],
                      fe_models_list_3[[1]], fe_models_list_4[[1]])

  etable_function(combined,
                cluster = c("stock_RIC", "month", "headquarters_country"),
                etable_title,
                sub_sample = periode_list,
                   "full_sample_regressions",
                file_name)
  return(combined)
}

###############################################################################
df_600_ex_50_list <- full_sample_function(df_600_ex_50, 
                     "Data: df_600_ex_50, Full Sample,",
                     "full_sample_df_600_ex_50.tex")

df_600_list <- full_sample_function(df_600, 
                     "Data: df_600, Full Sample,",
                     "full_sample_df_600.tex")

df_50_list <- full_sample_function(df_50, 
                     "Data: df_50, Full Sample,",
                     "full_sample_df_50.tex")

###############################################################################
merged_list <- append(df_600_list, df_50_list)
merged_list <- append(merged_list, df_600_ex_50_list)

etable_function(merged_list, cluster = c("stock_RIC", "month"),
                              "Data: df_600, df_50, df_600_ex_50, Full Sample",
                              sub_sample = list(c(2011, 2024)),
                              "full_sample_regressions",
                              "full_sample_final.tex")

```

### Sample split by period
```{r}
#################################################################
# Data: df and df_outstanding
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m",
                "final_INDEX_FUND_ownership", "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2011, 2013), 
                    c(2013, 2015),
                    c(2015, 2017), 
                    c(2017, 2020), 
                    c(2020, 2022), 
                    c(2022, 2024))

fe_models_list_5 <- data_on_fe_function(
  df_600,indep_vars, fixed_vars, period_list, setup = "lag")

etable_function(fe_models_list_5, 
                cluster = c("stock_RIC"),
                "Data: df_600,",
                sub_sample = period_list,
                "sample_split_regressions",
                "sample_split_table_5.tex")

#################################################################
fixed_vars <- c("stock_RIC","month", "headquarters_country")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m",
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2011, 2015), c(2015, 2020), c(2020, 2024))

fe_models_list_8 <- data_on_fe_function(
  df_600, indep_vars, fixed_vars, period_list, setup = "lag")

etable_function(fe_models_list_8,
                cluster = c("stock_RIC", "headquarters_country"),
                   "Data: df_outstanding",
                 sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_split_table_9.tex")


#################################################################
# Data: df and df_outstanding
#################################################################
fixed_vars <- c("stock_RIC", "quarter")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m",
                "final_INDEX_FUND_ownership", "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2011, 2014), c(2014, 2017), c(2017, 2020),
                    c(2020, 2024))

fe_models_list_7 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "lag")
etable_function(fe_models_list_7,
                cluster = fixed_vars,
                   "Data: df_index",
                sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_equal_split_df_outstanding_v2.tex")
```

### Complete sample split
```{r}
fixed_vars <- c("stock_RIC")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread", "price_to_BV",
                "cumulative_return_12m", "final_FUND_ownership",
                "final_INDEX_FUND_ownership", "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2011, 2012) , c(2012, 2013), c(2013, 2013), 
                    c(2014, 2015), c(2015, 2016), c(2016, 2017), c(2017, 2018),
                    c(2018, 2019), c(2019, 2020), c(2020, 2021), c(2021, 2022),
                    c(2022, 2023))

fe_models_list_5 <- data_on_fe_function(
  df_50,indep_vars, fixed_vars, period_list, setup = "lag")

etable_function(fe_models_list_5, 
                cluster = c("stock_RIC"),
                "Data: df_50,",
                sub_sample = period_list,
                "sample_split_regressions",
                "sample_split_table_5.tex")
```


### fund only regressions
```{r}
#################################################################
# Data: df, 2018
#################################################################
fixed_vars <- c("month", "stock_RIC")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership",
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2010, 2015), c(2015, 2020), c(2020, 2024))

fe_models_list_7 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")
etable_function(fe_models_list_7,
                   "Data: df_outstanding",
                sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_split_df_outstanding_fund_split.tex")
```

### new fixed effects
```{r}
#################################################################
# Data: df_outstanding, country fixed effects
#################################################################
fixed_vars <- c("headquarters_country", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership",
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2010, 2015), c(2015, 2020), c(2020, 2024))

fe_models_list_8 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "lag")
  
etable_function(fe_models_list_8,
                title = "Data: df_outstanding",
                sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_split_df_outstanding_country_fixed.tex")

#################################################################
# Data: df_outstanding, industry fixed effects
#################################################################
fixed_vars <- c("economic_sector", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership",
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2011, 2015), c(2015, 2020), c(2020, 2024))

fe_models_list_9 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "lag")
  
etable_function(fe_models_list_9,
                title = "Data: df_outstanding",
                sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_split_df_outstanding_industry_fixed.tex")

#################################################################
# Data: df_outstanding, country fixed and industry fixed
#################################################################
fixed_vars <- c("stock_RIC", "month")
indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership",
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2011, 2013), c(2013, 2017), c(2020, 2021), c(2021, 2024))
#period_list <- list(c(2010, 2012), c(2012, 2014), c(2014, 2016),
                    #c(2016, 2018), c(2018, 2020), c(2020, 2022))

fe_models_list_10 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "lag")
  
etable_function(fe_models_list_10,
                title = "Data: df_outstanding",
                sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_split_df_outstanding_country_industry_fixed.tex")

#################################################################
# Data: df_outstanding, year fixed effects
#################################################################

indep_vars <- c("final_ETF_ownership",
                "log_market_cap", "inv_price", "amihud_ratio",
                "monthly_relative_spread",
                "cumulative_return_12m", "final_INDEX_FUND_ownership",
                "final_ACTIVE_FUND_ownership",
                "final_T1_monthly_std_dev", "final_T2_monthly_std_dev",
                "final_T3_monthly_std_dev")

period_list <- list(c(2010, 2024))

##################
fixed_vars <- c("stock_RIC", "month")
fe_models_list_11 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")

fixed_vars <- c("stock_RIC", "year")
fe_models_list_12 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")
##################
fixed_vars <- c("economic_sector", "month")
fe_models_list_13 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")
##################
fixed_vars <- c("headquarters_country", "month")
fe_models_list_15 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")

fixed_vars <- c("headquarters_country", "economic_sector", "month")
fe_models_list_16 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")
##################
fixed_vars <- c("headquarters_country", "economic_sector", "year")
fe_models_list_17 <- data_on_fe_function(df_outstanding,
                                        indep_vars, fixed_vars,
                                        period_list, setup = "single")

  
etable_function(list(fe_models_list_11[[1]], fe_models_list_12[[1]],
                     fe_models_list_13[[1]],
                     fe_models_list_15[[1]], fe_models_list_16[[1]],
                     fe_models_list_17[[1]]),
                title = "Data: df_outstanding",
                sub_sample = period_list,
                   "sample_split_regressions",
                   "sample_split_df_outstanding_full_sample_fixed_effects.tex")
```

# stock level data check
## monthly std check
```{r}
df_stock_level <- read.csv("/Users/jonathanzeh/Library/CloudStorage/OneDrive-Personal/BA_Thesis/BA_coding/datasets/eikon_data/stock_level_data/stock_level_data.csv")

df_zurich <- df_stock_level %>%
  filter(stock_RIC == "ZURN.S") %>%
  mutate(date = as.Date(date),
    year_month = format(date, "%Y-%m"))

monthly_sd <- df_zurich %>%
  group_by(year_month) %>%
  summarize(monthly_sd = sd(return0D))

plot(df_50$date, df_50$monthly_std_dev, col = rgb(0, 0, 1, 0.1))
plot(df_600$date, df_600$monthly_std_dev, col = rgb(0, 0, 1, 0.01), ylim=c(0, 0.12))
plot(df_600$date, df_600$final_monthly_std_dev, col = rgb(0, 0, 1, 0.03))
abline(a=mean(df_600$monthly_std_dev, na.rm = TRUE), b=0, col = "red")
```

## return1D check
```{r}
df_zurich <- df_zurich %>%
  mutate(return_old = return1D / 100,
         return_check = price/lag(price) - 1,
         return_ln_check = log(price/lag(price)))
```


## amihud check
```{r}
df_zurich <- df_zurich %>%
  mutate(amihud = 10^6 * abs((return_check / 100)) / (volume * price))


df_zurich %>%
  group_by(year_month) %>%
  summarize(monthly_amihud = mean(amihud))
```


# old code
## old: implement fixed effects function
```{r}
data_on_fe_function <- function(df, indep_vars, fixed_vars, periode_list){
  fe_model_1 <- fe_function(df, indep_vars, fixed_vars,
                                    periode_list[[1]], volatility_lag = FALSE)
  fe_model_1_lag <- fe_function(df, indep_vars, fixed_vars,
                                        periode_list[[1]], volatility_lag = TRUE)
  
  fe_model_2 <- fe_function(df, indep_vars, fixed_vars,
                               periode_list[[2]], volatility_lag = FALSE)
  fe_model_2_lag <- fe_function(df, indep_vars, fixed_vars,
                                   periode_list[[2]], volatility_lag = TRUE)
  
  fe_model_3 <- fe_function(df, indep_vars, fixed_vars,
                                    periode_list[[3]], volatility_lag = FALSE)
  fe_model_3_lag <- fe_function(df, indep_vars, fixed_vars,
                                        periode_list[[3]], volatility_lag = TRUE)
  
  fe_models_list <- list(fe_model_1 = fe_model_1,
                         fe_model_1_lag = fe_model_1_lag,
                         fe_model_2 = fe_model_2,
                         fe_model_2_lag = fe_model_2_lag,
                         fe_model_3 = fe_model_3,
                         fe_model_3_lag = fe_model_3_lag)
  return(fe_models_list)
}

```


## stargazer function
```{r}
library(stargazer)

stargazer_function <- function(fe_models_list, variables, title_vector, 
                               subfolder, file_name) {
  folder_path = "/Users/jonathanzeh/Library/CloudStorage/OneDrive-Personal/BA_Thesis/BA_coding/R_exports/regression_outputs/"
  
  output_path_lag = paste0(folder_path, subfolder, "/", file_name, "_lag.tex")
  output_path_no_lag = paste0(folder_path, subfolder, "/", file_name, "_no_lag.tex")
  
  # with volatility lags
  latex_code <- stargazer(fe_models_list[[4]], 
                          fe_models_list[[4]], 
                          fe_models_list[[6]],
            
            type = "latex",
            title = title_vector[1],
            dep.var.labels = c("Daily Volatility (t)"),
            column.labels = c("2010 to 2019", "2020", "2021 to 2023"),
            covariate.labels = variables,
            omit.stat = c("f", "ser"),
            add.lines = list(c("Month fixed effects", 
                               "Yes", "Yes", "Yes"),
                             c("Stock fixed effects", 
                               "Yes", "Yes", "Yes")),
            out = output_path_lag)
  
    # without volatility lags
    variables = variables[-((length(variables)-2):length(variables))]
    latex_code <- stargazer(fe_models_list[[1]], 
                            fe_models_list[[2]], 
                            fe_models_list[[3]],
            
            type = "latex",
            title = title_vector[2],
            dep.var.labels = c("Daily Volatility (t)"),
            column.labels = c("2010 to 2019", "2020", "2021 to 2023"),
            covariate.labels = variables,
            omit.stat = c("f", "ser"),
            add.lines = list(c("Month fixed effects", 
                               "Yes", "Yes", "Yes"),
                             c("Stock fixed effects", 
                               "Yes", "Yes", "Yes")),
            out = output_path_no_lag)
}
```
